Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-22 finnormal-nodalida-2015/finnormal2015.tex
update table
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58530 72bbbca6-d526-0410-a7d9-f06f51895060
add citations to two papers
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58533 72bbbca6-d526-0410-a7d9-f06f51895060

\documentclass[11pt]{article}
\usepackage{nodalida2015}
%\usepackage{times}
\usepackage{mathptmx}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{latexsym}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

\begin{table}
  \centering
 \begin{tabular}{|l|r|}
    \hline
    \textbf{Section} & \textbf{Tokens} \\
    \hline
    \texttt{train} & 2,538 \\
    \texttt{test} & 1,012 \\
    \texttt{dev} & 1,003 \\
    \hline
 \end{tabular} 
  \caption{Statistics on sentences from the parallel corpus.}
  \label{table:corpsize}
\end{table}

\begin{table*}
  \centering
  \begin{tabular}{|l|l|l|}
  \hline
  \textbf{Colloquial} & \textbf{Normalised} & \textbf{Standardised} \\
  \hline
  mut siis, oli siell\"{a} jotain vaikka     & mutta siis, oli siell\"{a} jotain vaikka     & mutta oli siell\"{a} jotain     \\
  puheteknologiamatskuja.  & puheteknologiamateriaaleja. & puheteknologiamateriaaleja.  \\
  \hline
  oon tosi hy\"{o}dyllinen assari     & ole todella hy\"{o}dyllinen assistentti & ole todella hy\"{o}dyllinen assistentti \\
  t\"{a}n vikan minuutin.           & t\"{a}m\"{a}n viimeisen minuutin.            & t\"{a}m\"{a}n viimeisen minuutin. \\
  \hline
  \ldots & \ldots & \ldots \\
  \hline
  \end{tabular}
  \caption{Example sentences from the parallel corpus.}
  \label{table:corpexample}
\end{table*}

@@

@@

@@

Joonas Kyl\"{a}m\"{a}

>>>>

\documentclass[11pt]{article}
\usepackage{nodalida2015}
%\usepackage{times}
\usepackage{mathptmx}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{multirow}
\usepackage{latexsym}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

\begin{table}
  \centering
 \begin{tabular}{|l|r|r|r|}
    \hline
    \multirow{2}{*}{\textbf{Section}} & \multicolumn{3}{|c|}{\textbf{Tokens}} \\\cline{2-4}
                                      & \texttt{train} & \texttt{test} & \texttt{dev} \\
    \hline
    Colloquial                           & 2,538 & 1,012 & 1,003 \\ 
    Normalised                           & 2,538 & 1,012 & 1,003 \\ 
    Standardised                         & 2,476 & 991 & 1,000 \\
    \hline
 \end{tabular} 
  \caption{Statistics on sentences from the parallel corpus.}
  \label{table:corpsize}
\end{table}

\begin{table*}
  \centering
  \begin{tabular}{|l|l|l|}
  \hline
  \textbf{Colloquial} & \textbf{Normalised} & \textbf{Standardised} \\
  \hline
  mut siis, oli siell\"{a} jotain vaikka     & mutta siis, oli siell\"{a} jotain vaikka     & mutta oli siell\"{a} jotain     \\
  puheteknologiamatskuja.  & puheteknologiamateriaaleja. & puheteknologiamateriaaleja.  \\
  \hline
  oon tosi hy\"{o}dyllinen assari     & olen todella hy\"{o}dyllinen assistentti & olen todella hy\"{o}dyllinen assistentti \\
  t\"{a}n vikan minuutin.           & t\"{a}m\"{a}n viimeisen minuutin.            & t\"{a}m\"{a}n viimeisen minuutin. \\
  \hline
  \ldots & \ldots & \ldots \\
  \hline
  \end{tabular}
  \caption{Example sentences from the parallel corpus.}
  \label{table:corpexample}
\end{table*}

@@

CBMT: \cite{TiedemannEAMT2009, TiedemannEACL2012}

@@

The idea behind this was that the \emph{normalised} part of the corpus would be

@@

Joonas Kylm\"{a}l\"{a}
